---
title: "LiveSessionUnit5Assignment"
author: "IramB"
date: "December 2, 2017"
output: html_document
---

## import the .txt file into R.  Assign the resulting data frame to an object, df, that consists of three columns with humanreadable column names for each 
```{r}
df <- read.table("C:/Users/DataScience/Documents/SMU/Data_Science/Unit_5/HW/yob2016.txt", sep=';')
colnames(df) <- c("Name","Gender","Amount of Children")

```

## Display the summary and structure of df 
```{r}
summary(df)
str(df)

```

## One name was entered twice and misspelled
```{r}
misspelled <- grep("yyy$", df$Name, value = TRUE)
misspelled
```

## please remove this misspelled name.  Save the remaining dataset as an object: y2016  
```{r}
ind <- which(with(df, (Name==misspelled)))
y2016 <- df[-ind, ]
```

## import the .txt file into R. 
```{r}
y2015 <- read.table("C:/Users/DataScience/Documents/SMU/Data_Science/Unit_5/HW/yob2015.txt", sep=',')
colnames(y2015) <- c("Name", "Gender", "Amount of Children")
```

##  Display the last ten rows in the dataframe. Describe Something interesting. It was interesting to see all names begin with the letter Z, all children were male and there were 5 children each with the name
```{r}
y2015[c((nrow(y2015) - 10): nrow(y2015)),]
```
Data is sorted by Name.


## Merge y2016 and y2015 by your Name column; assign it to final
```{r}
final <- merge(y2015, y2016, by=c('Name', 'Gender'))
names(final) <- c('Name', 'Gender', 'Count2015', 'Count2016')
```


## Create a new column called "Total" in final that adds the amount of children in 2015 and 2016 together. 
```{r}
final$Total <- final$Count2015 + final$Count2016
```
## In those two years combined, 7239231 people were given popular names 
```{r}
sum(final$Total)
```
## Sort the data by Total.  What are the top 10 most popular names
```{r}
final <- final[order(final$Total, decreasing=TRUE),]
final$Name[c(1: 10)]
```

##  Omit boys and give the top 10 most popular girl's names. Assign this to object girl
```{r}
males <- final$Gender=='M'
finalfemales <- final[!males,]
girl <- final[final$Gender == 'F', 'Name'][c(1: 10)]

```

## Write these top 10 girl Names and their Totals to a CSV file called itsagirl.csv. 
```{r}

itsagirl <- data.frame(Name=girl, Total=final[final$Gender == 'F', 'Total'][c(1: 10)])
write.csv(itsagirl, 'itsagirl.csv', row.names=FALSE)
```


